Pillar 2 - Topic Modeling

### 2019-01-10 Pillar 2 - Topic Modeling.Rmd
minor changes

---
title: "Pillar 2 - Topic Modeling"
output: github_document:
  number_section: TRUE
---

@@

# TF-IDF
# TF-IDF
```{r function make_barplot and make_WC, out.height=8, out.width=16}
make_barplot <- function(data, facet, n_col = 5){

@@

>>>>

---
title: "Pillar 2 - Topic Modeling"
output: github_document
---

@@

# TF-IDF
## Functions for Generating Barplots and Word Clouds
```{r function make_barplot and make_WC, out.height=8, out.width=16}
make_barplot <- function(data, facet, n_col = 5){

@@

## Course Level
```{r tf-idf per course}
tdm_top <- d_overview_stem %>%
  filter(`Calendar Year` == "2018-2019") %>%
  count(Code, `Calendar Year`, word, sort = T) %>%
  bind_tf_idf(term = word, document = Code, n = n) %>%
  filter(n >= 2) %>%
  group_by(Code) %>%
  top_n(10, tf_idf) %>%
  ungroup %>%
  filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) # select 25 courses at random

make_barplot(data = tdm_top, facet = Code)
make_WC(data = tdm_top, facet = Code)
```

## Cluster Level
```{r tf-idf per cluster}
tdm_top <- d_overview_stem %>%
  left_join(select(d_course, Code, Cluster), by = "Code") %>%
  filter(`Calendar Year` == "2018-2019",
         !is.na(Cluster)) %>%
  count(Cluster, `Calendar Year`, word, sort = T) %>%
  bind_tf_idf(term = word, document = Cluster, n = n) %>%
  filter(n >= 5) %>%
  group_by(Cluster) %>%
  top_n(10, tf_idf) %>%
  ungroup

# Plots
make_barplot(data = tdm_top, facet = Cluster, n_col = 4)
make_WC(data = tdm_top, facet = Cluster, n_col = 4)
```

## Concentration Level
```{r tf-idf per concentration}
tdm_top <- d_overview_stem %>%
  left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
  gather(key = "key", value = Concentration,
         c("Concentration", "Concentration (additional)"),
         na.rm = T) %>%
  filter(`Calendar Year` == "2018-2019") %>%
  count(Concentration, `Calendar Year`, word, sort = T) %>%
  bind_tf_idf(term = word, document = Concentration, n = n) %>%
  filter(n >= 5) %>%
  group_by(Concentration) %>%
  top_n(10, tf_idf) %>%
  ungroup

# Plots
make_barplot(data = tdm_top, facet = Concentration)
make_WC(data = tdm_top, facet = Concentration)
```

# LDA

## Fitting Model
